Automated discovery of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Update ms.tex

>>>>

Although we focus on GW in this work, the method can be easily extended to other population analysis.
For example, given the recently release Gaia DR3 data \cite{2016A&A...595A...1G}, , we can apply our method to understanding the population of stars without much augmentation to the pipeline.
As size of data sets grows larger in astronomy, this work provides a simple and scalable pathway to uncover trends and relations in astrophysical catalogs.
